Peer influences in air travel behavior: A social autoregressive analysis

### 2015-04-24 article/article.Rmd
Added more math formatting.

Methodology
======================================
We introduce social dependence into a Poisson count model that predicts the
number of airline trips an individual makes as a function of his or her
socioeconomic variables. The Poisson count model estimates the effect of
dependent variables  on the conditional mean number of trips, . We consider
social interaction in this model by suggesting that  (where  is the row of  that
contains the weights for the neighbors of ). Our goal in this analysis is to
recover a weighting scheme  that maximizes the model likelihood, and use this
model to examine the inferential error that could result from ignoring social
interdependence and correlation in such model.

>>>>

Methodology
======================================
We introduce social dependence into a Poisson count model that predicts the
number of airline trips an individual makes as a function of his or her
socioeconomic variables. The Poisson count model estimates the effect of
dependent variables $X_i$ on the conditional mean number of 
trips, $\lambda_i = e^{X_i\beta}$. This mean in turn determines the probability 
of a discrete number of event occurrences,

$$P(y_i = y | X) = \frac{\lambda_i e^{-\lambda_i}}{y!}$$

We consider the influence of social interaction in this model by suggesting

$$\lambda_i = e^{\rho W_i y + X_i\beta + W_iX_i \gamma}$$.

If the $\rho$ and $\gamma$ parameters are statistically significant, this 
indicates air travel is *socially dependent*, or that it is influenced by factors
that are socially dependent. Further, if the parameters on this model are 
significantly different from the non-social model, it implies that a non-social
model may return biased parameters and/or inaccurate inferences.

### Software
